Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-14 ieee_paper.tex
comments

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
                           & v1m1  & v1m4  & v4m1   & v4m4  \\
    \hline
    Best Single Precision  & 36.36 & 58.18 & 133.33 & 213.33\\
    Worst Single Precision &  4.15 & 14.20 &  16.55 &  55.81\\
    Best Double Precision  & 24.00 & 32.21 &  85.71 & 117.07\\
    Worst Double Precision &  3.93 & 11.88 &  15.58 &  46.15\\
    \hline
  \end{tabular}

  \caption{Estimation of performance in GFlop/s at 150GB/s for a matrix of $n_z = 32$}
\end{table}

  \centering 
  \subfigure[Peak performance of SpMV algorithm assuming either 1 or 4
    matrices and/or vectors. We used a memory bandwidth of 150
    Gbytes/sec (based on measurements in a code similar to the SpMV
    kernel, with computations
    removed).]{\includegraphics[width=.49\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops_peak_perf}}
%
  \subfigure[Speedup relative to base case using one matrix and one
    vector.]{\includegraphics[width=.49\linewidth]{figures/speedup_wrt_base.pdf}\label{fig:speedup}}

  \caption{\todo{to write}}

>>>>

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|r|}
    \hline
                           & v1m1  & v1m4  & v4m1   & v4m4  \\
    \hline
    Best Single Precision  & 36.36 & 58.18 & 133.33 & 213.33\\
    Worst Single Precision &  4.15 & 14.20 &  16.55 &  55.81\\
    Best Double Precision  & 24.00 & 32.21 &  85.71 & 117.07\\
    Worst Double Precision &  3.93 & 11.88 &  15.58 &  46.15\\
    \hline
  \end{tabular}
  \caption{Estimation of performance in GFlop/s at 150GB/s for a
    matrix of $n_z = 32$}
\end{table}

\begin{figure*}
  \centering 
  \subfigure[Absolute performance ]{\includegraphics[width=.49\linewidth]{figures/gflops_peak.pdf}\label{fig:gflops_peak_perf}}
%
  \subfigure[Relative performance to base case using one matrix and one
    vector.]{\includegraphics[width=.49\linewidth]{figures/speedup_wrt_base.pdf}\label{fig:speedup}}

  \caption{Estimation of the reachable performance one can
      achieve using a device with a memory to computational units of
      150GB/s when varying the number of vectors and matrices}
  \label{fig:perf_predict}
\end{figure*}

\todo{conclude on the evaluation using the figure/table. Note that we
  base prediction on 150GB/s which is not the peak of saule12. Note
  that if you are in best in v1m1 you might go to bad v4m4, but if you
  are in bad v1m1, you will essentially stay there.}
